Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-11 paper/paper.tex
Rewrote explanation in 4.1

Qualitatively this result can be understood as follows. 
The broad \lya line is the result of subsequent \lya photon
scatterings due to (relatively) fast moving clumps while the
multi-phase nature (i.e., the existence of low-density inter-clump
regions where \lya photons can freely prograpagate)  ensures the high
flux at line center as observed.   
In turn, a lower velocity dispersion would produce a thiner line than
it is observed.
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms. 
This is also supported by the classification tree example in Figure
\ref{fig:tree}.

As a test, we also run a small set of 100 additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are within the derived
constraints.
Consistent with the results from the random forest algorithm,
illustrated by the classification tree of Figure \ref{fig:tree}, we
find that $30$ models show $\chi^2/d.o.f.<35$.

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Even if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example in Figure
\ref{fig:tree} shows.

>>>>

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the moving clumps ($P_{\rm cl}$), the `intrinsic' profile represents the kinematics of the clumps, that is, the width of the intrinsic line is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by $v_{\infty}$ \& $\beta_{\rm cl}$.
Furthermore, the relatively low mean number of clumps per line of sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion of the clumps implies the 
existence of low-density inter-clump
regions where \lya photons can freely propagate which leads to an emergent spectrum close to the intrinsic one as well as to the high flux at line center as observed.
Because the width of the observable spectrum is hence set primarily by $\sigma_{\rm cl}$, a lower velocity dispersion would produce a narrower line and thus a worse fit.
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms. 
This is also supported by the classification tree example in Figure
\ref{fig:tree}.

As a test, we also run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1-\sigma$
constraints. \mg{Is $1\sigma$ correct?}
Consistent with the results from the random forest algorithm,
illustrated by the classification tree of Figure \ref{fig:tree}, we
find that $30$ models show $\chi^2/d.o.f.<35$.

Having constrained only 3 parameters, one might wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Even if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example in Figure
\ref{fig:tree} shows.
